Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-14 WSSSPE2_report/WSSSPE2_review.tex
fixing a typo - also, need to remind other lightning talk speakers to contribute summaries
Section 4: Add raw summary.

Lightning talks were a new feature in WSSSPE2. Since the workshop program was
mostly dedicated to discussions, the organizers wanted to give the attendees a
chance to also `make a pitch' for an idea, either representing a contributed paper
or something different.  Eighteen attendees volunteered to participate in the lightning
talks, each given only two minutes to speak and at most one slide to show.
The talks were presented in reverse alphabetic order of speakers' last names. 
In the rest of this session, we highlight the gist of some of the speakers' messages.

@@

%\item John W Peterson: Continuous Integration for Concurrent MOOSE Framework and
%Application Development on GitHub

>>>>

Lightning talks were a new feature in WSSSPE2. Since the workshop program was
mostly dedicated to discussions, the organizers wanted to give the attendees a
chance to also `make a pitch' for an idea, either representing a contributed paper
or something different.  Eighteen attendees volunteered to participate in the lightning
talks, each given only two minutes to speak and at most one slide to show.
The talks were presented in reverse alphabetic order of speakers' last names. 
In the rest of this section, we highlight the gist of some of the speakers' messages.

@@

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub}

%Affiliation: Idaho National Laboratory

In March 2014, the MOOSE framework was released under an open
source license on GitHub, significantly expanding and diversifying the pool of
current active and potential future contributors on the project. The MOOSE team
employs an extensive continuous integration test suite to ensure that both the
framework, and the applications based on the framework, are verified before any
code changes are accepted into the repository. We use a combination of built-in
git features such as branching and submodules, GitHub API integration
capabilities, and in-house developed testing software to both perform this
verification and update the dependent applications in a relatively seamless
manner for users.
